### 2017-07-06 paper/exp_appendix.tex
changes to experiments

\section{Experimental Results}\label{sec:app_ex}
% The table which is to be there in appendix
In Table~\ref{tab:exp1} in Section~\ref{} we presented results for twenty five benchmarks.
We now present additional result for other twenty seven benchmarks in Table~\ref{tab:exp3}.

@@

   {Benchmark} & {Time (s)} & {Solution} & {Dimension} & {Prob. loops} & {Prob. Assignments
} \\\hline
{aaron2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{ax} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{complex} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{counterex1b} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{cousot9} & {0.08} & {yes} & {3} & {yes} & {no
} \\\hline
{easy2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{loops} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{nestedloop} & {0.09} & {yes} & {3} & {yes} & {no
} \\\hline
{perfect1} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{random1d} & {0.08} & {yes} & {2} & {yes} & {yes
} \\\hline
{realbubble} & {0.18} & {yes} & {3} & {yes} & {yes
} \\\hline
{realheapsort} & {0.18} & {no} & {} & {no} & {no
} \\\hline
{realheapsort\_step1} & {0.09} & {no} & {} & {no} & {no
} \\\hline
{realselect} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{rsd} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{sipma91} & {0.11} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedDis1} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedFails1} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedFails4} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedNestedMultipleDep} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedpldi3} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedSimpleMultiple} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{speedSingleSingle} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{terminate} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{wcet0} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{wcet2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{wise} & {0.07} & {no} & {} & {no} & {no} \\\hline 
    \end{tabular}
    \caption{Caption}
    \label{tab:my_label}
\end{table}
\end{center}

>>>>

\section{Experimental Results}\label{sec:app_ex}
% The table which is to be there in appendix
In Table~\ref{tab:exp1} in Section~\ref{sec:experiments} we presented results for twenty five benchmarks.
We now present additional result for other twenty seven benchmarks in Table~\ref{tab:exp3}.

@@

   {Benchmark} & {Time (s)} & {Solution} & {Dimension} & {Prob. loops} & {Prob. Assignments
} \\\hline
{aaron2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{ax} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{complex} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{counterex1b} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{cousot9} & {0.08} & {yes} & {3} & {yes} & {no
} \\\hline
{easy2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{loops} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{nestedloop} & {0.09} & {yes} & {3} & {yes} & {no
} \\\hline
{perfect1} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{random1d} & {0.08} & {yes} & {2} & {yes} & {yes
} \\\hline
{realbubble} & {0.18} & {yes} & {3} & {yes} & {yes
} \\\hline
{realheapsort} & {0.18} & {no} & {} & {no} & {no
} \\\hline
{realheapsort\_step1} & {0.09} & {no} & {} & {no} & {no
} \\\hline
{realselect} & {0.09} & {yes} & {3} & {yes} & {yes
} \\\hline
{rsd} & {0.08} & {yes} & {1} & {yes} & {yes
} \\\hline
{sipma91} & {0.11} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedDis1} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedFails1} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{speedFails4} & {0.07} & {no} & {} & {no} & {no
} \\\hline
{speedNestedMultipleDep} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedpldi3} & {0.08} & {yes} & {3} & {yes} & {yes
} \\\hline
{speedSimpleMultiple} & {0.08} & {no} & {} & {no} & {no
} \\\hline
{speedSingleSingle} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{terminate} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{wcet0} & {0.09} & {yes} & {2} & {yes} & {yes
} \\\hline
{wcet2} & {0.07} & {yes} & {2} & {yes} & {yes
} \\\hline
{wise} & {0.07} & {no} & {} & {no} & {no} \\\hline 
    \end{tabular}
    \caption{Additonal experimental results for benchmarks from~\cite{ADFG10:lexicographic} extended with probabilistic loops and/or probabilistic assignments.}
    \label{tab:exp3}
\end{table}
\end{center}
